### 2023-03-08 manuscript.tex
Fixing and adding DOI for OSF and Dryad repositories [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ddd995f3f5e7c62f7171b6281520a9be8cf82da1.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ddd995f3f5e7c62f7171b6281520a9be8cf82da1/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366592231

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/172dcb1ccde7bbd26b6c3e3335201992dc5c131b/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/172dcb1ccde7bbd26b6c3e3335201992dc5c131b}{SORTEE-Github-Hackathon/manuscript@172dcb1}
on March 8, 2023.

@@

Government, funding agencies, and publishers exercise rigorous open access data policies and mandates (\protect\hyperlink{ref-1Hcf13Q0k}{Nugroho et al., 2015}; \protect\hyperlink{ref-PLmDFZrm}{Tenopir et al., 2020}).
However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons (\protect\hyperlink{ref-SLq38RVv}{Figueiredo, 2017}; \protect\hyperlink{ref-1CzUZwyU2}{Tenopir et al., 2015}; \protect\hyperlink{ref-1Ch6LSHef}{Wicherts et al., 2011}).
Still, data deposition and ensuring its availability can amplify the outreach of published studies (\protect\hyperlink{ref-666HppfO}{Pronk et al., 2015}), increase citation rates (\protect\hyperlink{ref-1CcAUn3Lu}{Piwowar et al., 2007}), and among many other reasons, enable the reproducibility and robustness of scientific advances (\protect\hyperlink{ref-1HZdsK5Kn}{Baker, 2016}; \protect\hyperlink{ref-uBJwnPbq}{Mislan et al., 2016}; \protect\hyperlink{ref-4LaijDIZ}{{``On Data Availability, Reproducibility and Reuse,''} 2017}).
While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
This is because GitHub, a for-profit company, does not have long-term data availability guarantees, allowing users to delete or make repositories private after publication.
Also, GitHub does not issue Digital Object Identifiers (DOI) for content uploaded to their servers.
DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally-stored research materials.
Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF (\protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}; \protect\hyperlink{ref-10ghgV3S8}{J. Perkel, 2016}); \protect\hyperlink{tbl:compare}{Table 1}).
Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}).
This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.}, the Zenodo repositores for Hudgins (\protect\hyperlink{ref-GQj3c17f}{2022}), EllenJCoombs (\protect\hyperlink{ref-bZNn2hbh}{2020}), and Lrharper1 (\protect\hyperlink{ref-ZI1OqZNr}{2018})).

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-bZNn2hbh}{}}%
EllenJCoombs. (2020). \emph{EllenJCoombs/Asymmetry-evolution-cetaceans-for-publication-v.1.0.0} (Version v.1.0.0) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.3893943}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ddd995f3f5e7c62f7171b6281520a9be8cf82da1/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ddd995f3f5e7c62f7171b6281520a9be8cf82da1}{SORTEE-Github-Hackathon/manuscript@ddd995f}
on March 8, 2023.

@@

Government, funding agencies, and publishers exercise rigorous open access data policies and mandates (\protect\hyperlink{ref-1Hcf13Q0k}{Nugroho et al., 2015}; \protect\hyperlink{ref-PLmDFZrm}{Tenopir et al., 2020}).
However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons (\protect\hyperlink{ref-SLq38RVv}{Figueiredo, 2017}; \protect\hyperlink{ref-1CzUZwyU2}{Tenopir et al., 2015}; \protect\hyperlink{ref-1Ch6LSHef}{Wicherts et al., 2011}).
Still, data deposition and ensuring its availability can amplify the outreach of published studies (\protect\hyperlink{ref-666HppfO}{Pronk et al., 2015}), increase citation rates (\protect\hyperlink{ref-1CcAUn3Lu}{Piwowar et al., 2007}), and among many other reasons, enable the reproducibility and robustness of scientific advances (\protect\hyperlink{ref-1HZdsK5Kn}{Baker, 2016}; \protect\hyperlink{ref-uBJwnPbq}{Mislan et al., 2016}; \protect\hyperlink{ref-4LaijDIZ}{{``On Data Availability, Reproducibility and Reuse,''} 2017}).
While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
This is because GitHub, a for-profit company, does not have long-term data availability guarantees, allowing users to delete or make repositories private after publication.
Also, GitHub does not issue Digital Object Identifiers (DOI) for content uploaded to their servers.
DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally-stored research materials.
Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF (\protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}; \protect\hyperlink{ref-10ghgV3S8}{J. Perkel, 2016}); \protect\hyperlink{tbl:compare}{Table 1}).
Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}).
This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.}, the Zenodo repositores Hudgins (\protect\hyperlink{ref-GQj3c17f}{2022}), Lrharper1 (\protect\hyperlink{ref-ZI1OqZNr}{2018}); the Dryad and OSF repositories Braga et al. (\protect\hyperlink{ref-xbM3u93u}{2023}) and Braga et al. (\protect\hyperlink{ref-TpcnPdJo}{2021})).

@@

\leavevmode\vadjust pre{\hypertarget{ref-TpcnPdJo}{}}%
Braga, P. H. P., Kembel, S., \& Peres-Neto, P. (2021). Code for: Historical and contemporary processes drive global phylogenetic structure across geographical scales: insights from bat communities. \emph{Open Science Framework}. \url{https://doi.org/10.17605/osf.io/amvp5}

\leavevmode\vadjust pre{\hypertarget{ref-xbM3u93u}{}}%
Braga, P. H. P., Peres-Neto, P., \& Kembel, S. (2023). \emph{Data for: Historical and contemporary processes drive global phylogenetic structure across geographical scales: Insights from bat communities} (Version 7) {[}Data set{]}. Dryad. \url{https://doi.org/10.5061/dryad.rjdfn2zgj}

@@
